---
title: "HW 1"
output: pdf_document
---

```{r}
# load package
library(readxl)
library(dplyr)
library(ggplot2)

## Load the data
df <- read.csv('Conjoint Data.csv')
head(df)
```

```{r}
# Getting the preference vector and design matrix
pre_all <- exam$Preference.Rank
design_matrix <- df[,2:6]
```


```{r}
# Conjoint Function
my_conjoint <- function(preferences, plotit=FALSE){
  
  # transform data types and store variables
  screen_75 <- factor(design_matrix$Screen.75.inch)
  screen_85 <- factor(design_matrix$Screen.85.inch)
  resolution_4k <- factor(design_matrix$Resolution.4K...1)
  sony <- factor(design_matrix$Sony...1)
  high_price <- factor(design_matrix$Price...low...0..high..1.)
  
  # run regression model and extract the coefficients
  model_reg <- lm(preferences~screen_75+screen_85+resolution_4k+sony+high_price)
  partworth <- coef(summary(model_reg))[,1]
  
  #############################################################
  # output 1: regression model summary for partworth, se, tval#
  #############################################################
  mod_summary <- coef(summary(model_reg))[,1:3]
  
  #################################
  # output 2: attribute importance#
  #################################
  attr_importance <- data.frame(matrix(NA, nrow=4, ncol=2))
  colnames(attr_importance) <- c('Range', 'Importance')
  rownames(attr_importance) <- c('screen_size', 'resolution', 'brand','price')
  
  # attribute importance - Range
  attr_importance[1,1] <- max(mod_summary[2:3,1], 0) - min(mod_summary[2:3,1], 0)
  attr_importance[2,1] <- max(mod_summary[4,1], 0) - min(mod_summary[4,1], 0)
  attr_importance[3,1] <- max(mod_summary[5,1], 0) - min(mod_summary[5,1], 0)
  attr_importance[4,1] <- max(mod_summary[6,1], 0) - min(mod_summary[6,1], 0)
  
  # attribute importance - Importance
  attr_importance[1,2] <- attr_importance[1,1]/sum(attr_importance$Range)
  attr_importance[2,2] <- attr_importance[2,1]/sum(attr_importance$Range)
  attr_importance[3,2] <- attr_importance[3,1]/sum(attr_importance$Range)
  attr_importance[4,2] <- attr_importance[4,1]/sum(attr_importance$Range)
  
  ##############################
  # output 3: Willingess to Pay#
  ##############################
  Sony_design <- c(1,1,0,1,1,2500)
  Sharp_design <- c(1,0,1,1,0,2000)
  point_val <- (Sharp_design[6]-Sony_design[6])/partworth[6]
  WTP <- as.data.frame(point_val*partworth, col.names='WTP')
  
  ###############################
  # output 4: Willingness to Pay#
  ###############################
  price_saving <- 2500 - 2000
  util <- price_saving / abs(mod_summary[6,1])
  wtp <- data.frame(matrix(NA, nrow=4, ncol=1))
  colnames(wtp) <- c("Willingness To Pay")
  rownames(wtp) <- c('75" screen_size', '85" screen_size', 'resolution', 'brand')
  wtp[1,1] <- mod_summary[2,1] * util # WTP for 75" screen_size
  wtp[2,1] <- mod_summary[3,1] * util # WTP for 85" screen_size
  wtp[3,1] <- mod_summary[4,1] * util # WTP for 4k resolution
  wtp[4,1] <- mod_summary[5,1] * util # WTP for Sony brand name
  
  ####################################
  # output 5: conjoint analysis table#
  ####################################
 
   # create blank result matrix
  CA <- data.frame(matrix(NA, nrow=12, ncol=6))
  CA[,1] <- seq(1500, 2600, by=100)
  colnames(CA) <- c('price', 'utility_mydesign', 'market_share', 'sales', 'margin', 'profit')
  
  # use for loop to get all the results for each price
  for (i in 1:12){
    
    # create matrix for my_design, sony, sharp, and costs
    my_design <- c(1,0,1,0,0,CA[i,1])
    Sony <- c(1,1,0,1,1,2500)
    Sharp <- c(1,0,1,1,0,2000)
    costs <- c(1000,500,1000,250,250, NA)
    design_info <- rbind(partworth,my_design, Sony, Sharp, costs)
    colnames(design_info) <- c('intercept','screen_75','screen_85','resolution_4k','sony','high_price')
    
    # Utility
    CA[i,2] <- sum(design_info['partworth',1:5] * design_info['my_design',1:5])+ design_info['partworth',6]*((CA[i,1]-design_info['Sharp',6])/(design_info['Sony',6]-design_info['Sharp',6]))
    utility_sony <- sum(design_info['partworth',1:5] * design_info['Sony',1:5])+ design_info['partworth',6]*((design_info['Sony',6]-design_info['Sharp',6])/(design_info['Sony',6]-design_info['Sharp',6]))
    utility_sharp <- sum(design_info['partworth',1:5] * design_info['Sharp',1:5])+ design_info['partworth',6]*((design_info['Sharp',6]-design_info['Sharp',6])/(design_info['Sony',6]-design_info['Sharp',6]))
    
    # Market Share
    CA[i,3] <- exp(CA[i,2])/sum(exp(CA[i,2]),exp(utility_sony),exp(utility_sharp))
    
    # Sales
    market_size <- 100
    CA[i,4] <- market_size*CA[i,3]
    
    # Margin
    Net_cost <- sum(design_info['my_design',1:5]*design_info['costs',1:5])
    CA[i,5] <- CA[i,1]-Net_cost
    
    # Profit
    CA[i,6] <- CA[i,4]*CA[i,5]
  }
  
  #############################################
  # output 5: optimal price and maximum profit#
  ############################################
  # convert CA to dataframe
  df_CA <- as.data.frame(CA)
  
  max_profit_val <- max(df_CA$profit)
  max_profit <- sprintf('Maximum Profit: %f', max_profit_val)
  opt_price_val <- df_CA$price[CA$profit == max_profit_val]
  opt_price <- sprintf('Optimal Price: %.0f', opt_price_val)
  
  ####################
  # output 6: plotting#
  ####################
  if(plotit){
    
    # Price vs Sales
    plot1 <- ggplot(aes(x=price, y=market_share), data=df_CA) + geom_line() + xlab('Price') + ylab('Market Share') + ggtitle('Market Share vs Price')
    
    # Price vs Profit
    plot2 <- ggplot(aes(x=price, y=profit), data=df_CA) + geom_line() + xlab('Price') + ylab('Profit') + ggtitle('Profit vs Price')
    

    
    out_graph <- list(plot1, plot2)
    print(out_graph)
  }
  
  
  out_table <- list(mod_summary, attr_importance, wtp, CA, opt_price, max_profit)
  return(out_table)
  
}
```

```{r}
# call function
my_conjoint(pre_all, plotit = TRUE)
```

**Interpretation:**

1. Partworth: Partworth is numerical score that measures how much each attribute/feature influences the customer's decision to select an alternative. Partworths are the coefficients of the product features in our linear regression model. And tells us how the ranking/preference is related to a certain attribute. In our case case, 4K resolution is the most influential feature as having 4K resolution would make the ranking of the product go up by 5.4, keeping all the other attributes constant.

2. Attribute Importance: As the relative importance of each attribute, it shows which attributes of a product are more or less important when we make a purchase. Based on the value of importance, the most important attribute is resolution (35%) and the least important attribute is brand (14%). 

3. Willingness to pay: the conjoint shows that the customers are willing to pay pay \$317 more for TV with 75 inch screen, $514 more for TV with 85 inch screen, \$689 more for TV with 4K resolution, and \$271 more for TV with Sony brand. 

4. Optimal Price: The optimal price for "my design" is $2100, the price that would generate the most profit.

5. Maximum Profit: The maximum profit is \$18 which can be achieved if we set the price of "my design" at $2100.

6. Market share (as function of Price): As we increase the prices, market share decreases. This is as expected since consumers are generally price-motivated, the higher the price, the lower the demand. The market share is a mere 1.83e-03 at our optimal pricepoint.

7. Profit (as function of Price): The plot shows the profit generated at each price point - we break even at \$2000 and can generate the most profit at \$2100 (although profit is minimal).
